Bullet Groups as a test of $\Lambda$CDM

### 2014-03-04 paper/ms.tex
re-estructurando las secciones y subsecciones

We estimate the expected distribution of displacements between the two
dominant dark matter peaks in halos within a mass range corresponding
to galaxy groups. We find that the probability of finding a system
similar with displacements of $\sim$400 kpch$^{-1}$ is between 40\%
for z$=0$ and 60\% for z$=1$ and $\Lambda$CDM standard model, which
correspond to the observational constraint the object SL2S J08544-0121
that is  a gravitational lens found in the SL2S and located at
z$=0.35$. Given the larger abundance of groups with respect to
clusters, finding multi-modal groups and baryonic-dark matter
displacements.  
\end{abstract}

@@

@@

The configuration of the BGs in the simulations is shown in Figure
\ref{configuration}. There we depict a host and its most massive
sub-halo from in a particular case found at z$=0$. The arrows show the
position and the velocity vectors sub-halo in a frame of reference
where the main halo is at rest; thus  $\vec{v{}}=\vec{v}_{sub}-\vec{v}_{halo}$ and
$\vec{r}=\vec{r}_{sub}-\vec{r}_{halo}$.  The angle between these two
vectors characterized by,
\begin{equation}
  \mu\equiv
  \cos(\theta)=\frac{\vec{v{}}\cdotp{}\vec{r}}{\left\|\vec{v}{}\right\|
    \left\|\vec{r}\right\|} 
 \end{equation} 
%
encodes the geometry of the collision, i.e. cases of $|\mu|\approx 1$
can be considered as head-on collisions while $|\mu|\approx 0$
describe a grazing trajectory.

@@

As a first approximation there are two quantities that are available
from observations of these Bullet-like systems. The projected distance
between two dominand dark matter clumps and the ratio of the
galaxies' luminosities associated to them. From the simulation point
of view this can be translated into the 2D projected values of
$||\vec{r}||$, its value relative to the virial radius $\chi =
||\vec{r}||_{2D}/R_{\rm vir}$ and the ratio of the circular velocities of the two clumps $V_{\rm c,sub}/V_{\rm c,host}$. Then, in order to gain better insight we use
the sub-structure velocity as a fraction of the host's circular
velocity, $||\vec{r}||/V_{\rm c, host}$, as a mesure of the the strenght
of the interaction.  Finally, an even more detailed picture of the
collision can be obtained through the values of $\mu$.

All the physical quantities described above can be used to describe
the tree main stages in a bullet-like encounter. First, the sub-halo
crosses the virial radius of the host halo starting a head on
collission, $|\vec{r}|/R_{\rm vir}\approx 1$ and
$\mu\approx<0.0$. Second, as the sub-halo crosses for the first time
the center of the host halo $|\vec{r}|/R_{\rm vir} < 1.0$ and
$\mu>0.0$. Third, as the sub-halo reaches apogee and comes back to the
center of the halo $|\vec{r}|/R_{\rm vir} < 1.0$ and $\mu<0.0$. We use
this quantities in Section XXX to fully characterize the different
kind of interactions observed in the Bolshoi simulation.

mass ranges and number of host halos and substructures 
are summary in the Table \ref{table1}. Of all the possible
configurations that can be presented in Figure \ref{configuration}, we
are interested in estimate in the simulation the number  of Bullet
Groups that may be present in an Universe of 250 $h^{-1}$Mpc. For this
we selected  of the simulations all the substructures   
whose velocities indicate a movement out of the host halo. Each halo
in this sample has a quantity called $X_{off}$ that corresponds to the
distance halo center (the minimum of the gravitational potential) to
the center of mass normalized by the virial radius ($R_{vir}$). Values
of $X_{off}$ equal to zero indicate relaxed halos, while $X_{off}>0$
indicates the existence of perturbed halos which can be considered
candidates to be Bullet Groups and this ditribution is shown  in a
scatter plot in the Figure \ref{cos_theta1} and the distribution of
$\nu_{circ,Halo}/\nu_{circ,Sub}$ is shown in  Figure \ref{cos_theta2},
both figures for differents z.

\begin{table*}
\begin{center}
\begin{tabular}{ccccccc}\hline\hline
Sample       & Minimum $V_{\rm c}$         & Maximum $V_{\rm c}$          & \# Halos  & \# Halos  & \# Halos & \# Halos \\
             & \kms    & \kms  &   $z=0$   & $z=0.25$  & $z=0.5$  & $z=1$  \\\hline
Host   & 300\kms & XX &    400    &   362     &   310    &  192   \\ 
Sub-structure & 75\kms  & XX &    XX   &   XX     &   XX    &  XX   \\\hline
\end{tabular} 
\caption{Circular velocity ranges for the halos and subhalos at
  different redshifts.}  
\label{table1}
\end{center}
\end{table*}

\begin{figure}
\begin{center}
\includegraphics[width=0.45\textwidth]{Figures_eps/Bullet_Group.eps}
\end{center}
\caption{Configuration for a host halo (dashed circle) and
  sub-structure (black circle) in the sample.}  
\label{configuration}
\end{figure}

@@

\subsection{Cumulative Probability Distributions}
\label{cumulative_distribution}

>>>>

We estimate the expected distribution of displacements between the two
dominant dark matter peaks in halos within a mass range corresponding
to galaxy groups. We find that the probability of finding a system
similar with displacements of $\sim$400 \hkpc is between 40\%
for z$=0$ and 60\% for z$=1$ and $\Lambda$CDM standard model, which
correspond to the observational constraint the object SL2S J08544-0121
that is  a gravitational lens found in the SL2S and located at
z$=0.35$. Given the larger abundance of groups with respect to
clusters, finding multi-modal groups and baryonic-dark matter
displacements.  
\end{abstract}

@@

\begin{table*}
\begin{center}
\begin{tabular}{ccccccc}\hline\hline
Sample  & Minimum $V_{\rm c}$ & Maximum $V_{\rm c}$  & \# Halos & \#
Halos  & \# Halos & \# Halos \\ 
 & \kms    & \kms  &   $z=0$   & $z=0.25$  & $z=0.5$  & $z=1$  \\\hline
Host   & 300 & XX &    400    &   362     &   310    &  192   \\ 
Sub-structure & 75  & XX &    XX   &   XX     &   XX    &  XX   \\\hline
\end{tabular} 
\caption{Circular velocity ranges for the halos and subhalos at
  different redshifts.}  
\label{table1}
\end{center}
\end{table*}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.45\textwidth]{Figures_eps/Bullet_Group.eps}
\end{center}
\caption{Configuration for a host halo (dashed circle) and
  sub-structure (black circle) in the sample.}  
\label{fig:configuration}
\end{figure}

The configuration of the BGs in the simulations is shown in Figure
\ref{fig:configuration}. There we depict a host and its most massive
sub-halo from in a particular case found at z$=0$. The arrows show the
position and the velocity vectors sub-halo in a frame of reference
where the main halo is at rest; thus  $\vec{v{}}=\vec{v}_{sub}-\vec{v}_{halo}$ and
$\vec{r}=\vec{r}_{sub}-\vec{r}_{halo}$.  The angle between these two
vectors characterized by,
\begin{equation}
  \mu\equiv
  \cos(\theta)=\frac{\vec{v{}}\cdotp{}\vec{r}}{\left\|\vec{v}{}\right\|
    \left\|\vec{r}\right\|} 
 \end{equation} 
%
encodes the geometry of the collision, i.e. cases of $|\mu|\approx 1$
can be considered as head-on collisions while $|\mu|\approx 0$
describe a grazing trajectory.

@@

As a first approximation there are two quantities that are available
from observations of these Bullet-like systems. The projected distance
between two dominand dark matter clumps and the ratio of the
galaxies' luminosities associated to them. From the simulation point
of view this can be translated into the 2D projected values of
$||\vec{r}||$, its value relative to the virial radius $X_{\rm 2D}=
||\vec{r}||_{\rm 2D}/R_{\rm vir}$ and the ratio of the circular velocities
of the two clumps $V_{\rm c,sub}/V_{\rm c,host}$. In a higher degree
of detail, in order to gaint better insight we use
the sub-structure velocity as a fraction of the host's circular
velocity, $||\vec{r}||/V_{\rm c, host}$, as a mesure of the the strenght
of the interaction.  Finally, we also measure the geometry of each
interaction through the values for $\mu$.

All the physical quantities described above can be used to describe
the tree main stages in a bullet-like encounter. First, the sub-halo
crosses the virial radius of the host halo starting a head on
collission, $||\vec{r}||/R_{\rm vir}\approx 1$ and
$\mu\approx<0.0$. Second, as the sub-halo crosses for the first time
the center of the host halo $||\vec{r}||/R_{\rm vir} < 1.0$ and
$\mu>0.0$. Third, as the sub-halo reaches apogee and comes back to the
center of the halo $||\vec{r}||/R_{\rm vir} < 1.0$ and $\mu<0.0$. We use
this quantities in Section XXX to fully characterize the different
kind of interactions observed in the Bolshoi simulation.

\subsection{Separations and Relative Circular Velocities}
\label{fig:separations}

\subsection{Relative Velocities}
\label{fig:velocities}

\subsection{Collision Geometries}
\label{fig:geometry}

\section{Discussion}
\label{sec:discussion}
Strictly speaking our results apply to multimodal groups and the e
expected separation betwen dark matter clumps. [...]

Expected displacement between dark and baryonic components are better
described by systems where the collision already occurred.[...]
(comparison with the old bullet clusters paper?)

The expectations to quantify this effects observationally are
high. [...]

@@
